Exposure Consequences - Statistics and Figures

### 2018-05-10 ManuscriptMaterials.Rmd
small change

```{r create_svgs}
plotReachAftereffects(generateSVG=TRUE)
plotLocalization(classicOnline=TRUE, generateSVG=TRUE)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE)
```

>>>>

```{r create_svgs, cache=FALSE, include=FALSE}
plotReachAftereffects(generateSVG=TRUE)
plotLocalization(classicOnline=TRUE, generateSVG=TRUE)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE)
```
